Modern Graph Generators: A Survey

### 2018-09-30 comparison.tex
last pass on my side
pass on Table III
Fixed several cells in table

\begin{sidewaystable}
\scriptsize
\centering
\tbl{Key characteristics of the generators (part A)} {
\begin{tabular}{| c | p{2.2cm} | p{2cm} |  p{2.2cm} | l |  l | l | p{3cm} | p{1.4cm} | l | }
 \hline
           &   & \multicolumn{2}{c}{\textbf{Domain}}
               & \multicolumn{2}{|c|}{\textbf{Operations}}
               & \multicolumn{4}{c|}{\textbf{Configuration}}
               \\ \hline
           &  \textbf{Generator}
               & \textbf{Type}
               & \textbf{Target / sample}
               & \textbf{Read}
               & \textbf{Update}
               & \textbf{\rot{Properties}}
               & \textbf{Distributions}
			   & \textbf{Output}
               & \textbf{\rot{Distributed\ }}
               \\ \hline
\hline   % ====================== general graphs
\multirow{7}{*}{\rot{\textbf{General}}}
  & \cite{barabasi1999emergence} & fixed & & Y & N & Y &  & &  N  \\
\cline{2-10}
   & R-MAt & fixed & & Y & N & Y & power-law & &  N  \\
\cline{2-10}
  & GraphGen & fixed & N & Y & N & Y&  & & N   \\
\cline{2-10}
  & Graph 500  & fixed & Various Domains& Y & N & Y & power-law & &  Y  \\
\cline{2-10}
  & BTER  & N & N &   N &  & N & user-defined &  ? & Y  \\
\cline{2-10}
  & Darwini  & N & N &   N &  & N & user-defined &  ? & Y   \\
%  & Watts-Strogatz~\cite{watts1998collective} & fixed & & Y & N & Y &  & &  N  \\
%\cline{2-10}
\hline
\hline %  ======================  Semantic web
\multirow{20}{*}{\rot{\textbf{Semantic web}}}
 & LUBM & fixed & university  & fixed & N & Y & random (LCG) &  RDF & N   \\
\cline{2-10}
 & LBBM & extracted & Lehigh University BibTeX  & N & N & Y & Monte Carlo &  RDF & N   \\
\cline{2-10}
 & UOBM & fixed & university  & fixed & N & Y & random &  RDF & N   \\
\cline{2-10}
 & IIMB & fixed & movies  & N & N & Y & random &  RDF & N   \\
\cline{2-10}
 & BSBM & fixed & e-commerce  & fixed & N & Y & mostly normal &  RDF, relational & N   \\
\cline{2-10}
 & SP$^2$Bench & fixed & DBLP  & fixed & N & Y & based on DBLP  & RDF & N   \\
\cline{2-10}
 & \cite{Duan:2011:AOC:1989323.1989340} & extracted & -- & N & Y &N & -- &  RDF & N    \\
\cline{2-10}
 & DBPSB & extracted & DBpedia &  templates & N & Y & random &  RDF & N   \\
\cline{2-10}
 & LODIB & fixed & e-commerce &  N & N & Y & 44 types &  RDF & N   \\
\cline{2-10}
 & SIB & fixed & social network &  mixes & mix & Y & from real-world data &  RDF & N   \\
\cline{2-10}
 & Geographica & fixed & OpenStreetMap  & fixed + templates  & N & Y & -- &  RDF & N   \\
\cline{2-10}
 & WatDiv & schema-driven & user-defined  & templates & N & Y & uniform, normal, Zipfian &  RDF & N   \\
\cline{2-10}
 & RBench & extracted & DBLP, Yago  & templates & N & Y & from real-world data &  RDF & N  \\
\cline{2-10}
 & LDBC SPB & fixed & media  & mixes & N & Y & power law, skewed values, value correlation &  RDF & N  \\
\cline{2-10}
 & LinkGen & schema-driven & user-defined & templates & Y  & N & Gaussian, Zipfian& RDF & N\\
\hline
\end{tabular} }
\label{tab:comparisonCharacteristicsA}
\end{sidewaystable}

\begin{sidewaystable}
\scriptsize
\centering
\tbl{Key characteristics of the generators (part B)} {
\begin{tabular}{| c | p{2.2cm}| p{2cm} |  p{2.2cm} | l |  l | l | p{3cm} | p{1.4cm} | l | }
 \hline
           &   & \multicolumn{2}{c}{\textbf{Domain}}
               & \multicolumn{2}{|c|}{\textbf{Operations}}
               & \multicolumn{4}{c|}{\textbf{Configuration}}
               \\ \hline
           &  \textbf{Generator}
               & \textbf{Type}
               & \textbf{Target / sample}
               & \textbf{Read}
               & \textbf{Update}
               & \textbf{\rot{Properties}}
               & \textbf{Distributions}
			   & \textbf{Output}
               & \textbf{\rot{Distributed\ }}
               \\ \hline
\hline  % ======================  graph databases
\multirow{7}{*}{\rot{\textbf{GDBs}}}
  & XGDBench & fixed  & social network  & fixed & Y & Y & power-law &  MAG &  Y  \\
\cline{2-10}
  & gMark & schema-driven (internal schema) &  user-defined  & generated &  N  & Y & uniform, normal, zipfian &  N-triples & N    \\
\cline{2-10}
  & graphGen & pattern-driven (Cypher schema) & user-defined  & -- & -- & Y & -- &  property graphs & N   \\
\hline
\hline %  ======================   social networks
\multirow{8}{*}{\rot{\textbf{SNs}}}
 & \cite{Barrett:2009:GAL:1995456.1995598} & fixed & social network & N & N & Y & simulation-driven & -- &  -- \\
\cline{2-10}
 & \cite{Yao2011} & fixed & social network & N & N & N & power-law & -- & --  \\
\cline{2-10}
 & LinkBench & fixed & social network & Y & Y & Y & Facebook & -- & -- \\
\cline{2-10}
 & S3G2 & fixed & social network  & N & N  & Y & Facebook  & CSV, RDF & Y   \\
\cline{2-10}
 & \cite{Sukthankar-SocialInfo2014} & schema-driven & social-network & N & N & Y & power-law & CSV & N   \\
\cline{2-10}
 & LDBC SNB  & fixed & social network &  generated & Y  & Y & Facebook &  CSV, RDF & Y     \\
\cline{2-10}
  & \cite{Nettleton2016} & schema-driven & social network & N & N & Y & power-law & -- & N  \\
%\cline{2-10}
% & SNG  & Y & Y &   N &  & Y & power-law & ? &  ?   \\
%\cline{2-10}
% & Forest Fire  & N & Y   & N &  & N & power-law &  ? & N   \\
\hline
\hline   % ======================   graph analytics
\multirow{3}{*}{\rot{\textbf{Ana.}}}
  & HPC Scalable Graph Analysis & fixed & & Y & N& N& uniform & & N   \\
\cline{2-10}
  & Graphalytics & extracted & social network & Y& N& power law & & & N   \\
\hline
\hline   %  ======================  streaming
\multirow{2}{*}{\rot{\textbf{St.}}}
  & S2Gen & schema-driven & Social Network & Y & N & N & user-defined & RDF & N     \\
\cline{2-10}
  & RSPLab & schema-driven & Agnostic & Y & Y & N & user-defined & RDF & N     \\
%\cline{2-10}
%  & & & & & & & &  &   \\
\hline
\end{tabular} }
\label{tab:comparisonCharacteristicsB}
\end{sidewaystable}

@@

\begin{table}[h]
\scriptsize
\centering
\tbl{Overlapping of classes of generators} {
\begin{tabular}{| c | l | l | l | l | l | l | l | }
 \hline
           &  \textbf{Generator}
               & \textbf{\rot{General}}
               & \textbf{\rot{Semantic Web}}
               & \textbf{\rot{Graph databases\ }}
               & \textbf{\rot{Social networks}}
               & \textbf{\rot{Analytics}}
               & \textbf{\rot{Steaming}}
               \\ \hline
\hline   % ====================== general graphs
\multirow{6}{*}{\rot{\textbf{General}}}
  & \cite{barabasi1999emergence} & x & & & & & \\
\cline{2-8}
   & R-MAt    & x & & & & & \\
\cline{2-8}
  & GraphGen  & x & & & & & \\
\cline{2-8}
  & Graph 500 & x & & & & & \\
\cline{2-8}
  & BTER      & x & & & & & \\
\cline{2-8}
  & Darwini   & x & & & & & \\
\hline
\hline %  ======================  Semantic web
\multirow{15}{*}{\rot{\textbf{Semantic web}}}
 & LUBM  & & x & & & & \\
\cline{2-8}
 & LBBM  & & x & & & & \\
\cline{2-8}
 & UOBM  & & x & & & & \\
\cline{2-8}
 & IIMB & & x & & & & \\
\cline{2-8}
 & BSBM & & x & & & & \\
\cline{2-8}
 & SP$^2$Bench & & x & & & & \\
\cline{2-8}
 & \cite{Duan:2011:AOC:1989323.1989340} & & x & & & & \\
\cline{2-8}
 & DBPSB & & x & & & & \\
\cline{2-8}
 & LODIB & & x & & & & \\
\cline{2-8}
 & SIB & & x & & & & \\
\cline{2-8}
 & Geographica & & x & & & & \\
\cline{2-8}
 & WatDiv & & x & & & & \\
\cline{2-8}
 & RBench & & x & & & & \\
\cline{2-8}
 & LDBC SPB & & x & & & & \\
\cline{2-8}
 & LinkGen & & x & & & & \\
\hline
\hline  % ======================  graph databases
\multirow{3}{*}{\rot{\textbf{GDBs}}}
  & XGDBench & & & x & & & \\
\cline{2-8}
  & gMark & & & x & & & \\
\cline{2-8}
  & graphGen & & & x & & & \\
\hline
\hline %  ======================   social networks
\multirow{7}{*}{\rot{\textbf{SNs}}}
 & \cite{Barrett:2009:GAL:1995456.1995598} & & & & x & & \\
\cline{2-8}
 & \cite{Yao2011}  & & & & x & & \\
\cline{2-8}
 & LinkBench  & & & x & x & & \\
\cline{2-8}
 & S3G2  & & x & x & x & & \\
\cline{2-8}
 & \cite{Sukthankar-SocialInfo2014}  & & & & x & & \\
\cline{2-8}
 & LDBC SNB   & & x & x & x & & \\
\cline{2-8}
  & \cite{Nettleton2016}  & & & & x & & \\
\hline
\hline   % ======================   graph analytics
\multirow{2}{*}{\rot{\textbf{An.}}}
  & HPC Scalable Graph Analysis  & & & & & x & \\
\cline{2-8}
  & Graphalytics & & & & & x & \\
\hline
\hline   %  ======================  streaming
\multirow{2}{*}{\rot{\textbf{St.}}}
  & S2Gen & & & & & & x\\
\cline{2-8}
  & RSPLab & & & & & & x \\
%\cline{2-8}
%  & & & & & & \\
\hline
\end{tabular} }
\label{tab:overlapping}
\end{table}

>>>>

\begin{sidewaystable}
\scriptsize
\centering
\tbl{Key characteristics of the generators (part A)} {
\begin{tabular}{| c | p{2.2cm} | p{2cm} |  p{2.2cm} | l |  l | l | p{3cm} | p{1.4cm} | l | }
 \hline
           &   & \multicolumn{2}{c}{\textbf{Domain}}
               & \multicolumn{2}{|c|}{\textbf{Operations}}
               & \multicolumn{4}{c|}{\textbf{Configuration}}
               \\ \hline
           &  \textbf{Generator}
               & \textbf{Type}
               & \textbf{Target / sample}
               & \textbf{Read}
               & \textbf{Update}
               & \textbf{\rot{Properties}}
               & \textbf{Distributions}
			   & \textbf{Output}
               & \textbf{\rot{Distributed\ }}
               \\ \hline
\hline   % ====================== general graphs
\multirow{7}{*}{\rot{\textbf{General}}}
  & \cite{barabasi1999emergence} & fixed & & Y & N & Y &  & edge-list &  N  \\
\cline{2-10}
   & R-MAt & fixed & & Y & N & Y & power-law & edge-list &  N  \\
\cline{2-10}
  & GraphGen & fixed & N & Y & N & Y&  & & N   \\
\cline{2-10}
  & Graph 500  & fixed & Various Domains& Y & N & Y & power-law & &  Y  \\
\cline{2-10}
  & BTER & fixed & N &   N &  & N & user-defined & edge-list & Y  \\
\cline{2-10}
  & Darwini & fixed & N &   N &  & N & user-defined &  edge-list & Y   \\
%  & Watts-Strogatz~\cite{watts1998collective} & fixed & & Y & N & Y &  & &  N  \\
%\cline{2-10}
\hline
\hline %  ======================  Semantic web
\multirow{20}{*}{\rot{\textbf{Semantic web}}}
 & LUBM & fixed & university  & fixed & N & Y & random (LCG) &  RDF & N   \\
\cline{2-10}
 & LBBM & extracted & Lehigh University BibTeX  & N & N & Y & Monte Carlo &  RDF & N   \\
\cline{2-10}
 & UOBM & fixed & university  & fixed & N & Y & random &  RDF & N   \\
\cline{2-10}
 & IIMB & fixed & movies  & N & N & Y & random &  RDF & N   \\
\cline{2-10}
 & BSBM & fixed & e-commerce  & fixed & N & Y & mostly normal &  RDF, relational & N   \\
\cline{2-10}
 & SP$^2$Bench & fixed & DBLP  & fixed & N & Y & based on DBLP  & RDF & N   \\
\cline{2-10}
 & \cite{Duan:2011:AOC:1989323.1989340} & extracted & -- & N & Y &N & -- &  RDF & N    \\
\cline{2-10}
 & DBPSB & extracted & DBpedia &  templates & N & Y & random &  RDF & N   \\
\cline{2-10}
 & LODIB & fixed & e-commerce &  N & N & Y & 44 types &  RDF & N   \\
\cline{2-10}
 & SIB & fixed & social network &  mixes & mix & Y & from real-world data &  RDF & N   \\
\cline{2-10}
 & Geographica & fixed & OpenStreetMap  & fixed + templates  & N & Y & -- &  RDF & N   \\
\cline{2-10}
 & WatDiv & schema-driven & user-defined  & templates & N & Y & uniform, normal, Zipfian &  RDF & N   \\
\cline{2-10}
 & RBench & extracted & DBLP, Yago  & templates & N & Y & from real-world data &  RDF & N  \\
\cline{2-10}
 & LDBC SPB & fixed & media  & mixes & N & Y & power law, skewed values, value correlation &  RDF & N  \\
\cline{2-10}
 & LinkGen & schema-driven & user-defined & templates & Y  & N & Gaussian, Zipfian& RDF & N\\
\hline
\end{tabular} }
\label{tab:comparisonCharacteristicsA}
\end{sidewaystable}

\begin{sidewaystable}
\scriptsize
\centering
\tbl{Key characteristics of the generators (part B)} {
\begin{tabular}{| c | p{2.2cm}| p{2cm} |  p{2.2cm} | l |  l | l | p{3cm} | p{1.4cm} | l | }
 \hline
           &   & \multicolumn{2}{c}{\textbf{Domain}}
               & \multicolumn{2}{|c|}{\textbf{Operations}}
               & \multicolumn{4}{c|}{\textbf{Configuration}}
               \\ \hline
           &  \textbf{Generator}
               & \textbf{Type}
               & \textbf{Target / sample}
               & \textbf{Read}
               & \textbf{Update}
               & \textbf{\rot{Properties}}
               & \textbf{Distributions}
			   & \textbf{Output}
               & \textbf{\rot{Distributed\ }}
               \\ \hline
\hline  % ======================  graph databases
\multirow{7}{*}{\rot{\textbf{GDBs}}}
  & XGDBench & fixed  & social network  & fixed & Y & Y & power-law &  MAG &  Y  \\
\cline{2-10}
  & gMark & schema-driven (internal schema) &  user-defined  & generated &  N  & Y & uniform, normal, zipfian &  N-triples & N    \\
\cline{2-10}
  & graphGen & pattern-driven (Cypher schema) & user-defined  & -- & -- & Y & -- &  property graphs & N   \\
\hline
\hline %  ======================   social networks
\multirow{8}{*}{\rot{\textbf{SNs}}}
 & \cite{Barrett:2009:GAL:1995456.1995598} & fixed & social network & N & N & Y & simulation-driven & impl. not available &  -- \\
\cline{2-10}
 & \cite{Yao2011} & fixed & social network & N & N & N & power-law & impl. not available & --  \\
\cline{2-10}
 & LinkBench & fixed & social network & Y & Y & Y & Facebook & impl. not available & -- \\
\cline{2-10}
 & S3G2 & fixed & social network  & N & N  & Y & Facebook  & CSV, RDF & Y   \\
\cline{2-10}
 & \cite{Sukthankar-SocialInfo2014} & schema-driven & social-network & N & N & Y & power-law & CSV & N   \\
\cline{2-10}
 & LDBC SNB  & fixed & social network &  generated & Y  & Y & Facebook &  CSV, RDF & Y     \\
\cline{2-10}
  & \cite{Nettleton2016} & schema-driven & social network & N & N & Y & power-law & impl. not available & --  \\
%\cline{2-10}
% & SNG  & Y & Y &   N &  & Y & power-law & ? &  ?   \\
%\cline{2-10}
% & Forest Fire  & N & Y   & N &  & N & power-law &  ? & N   \\
\hline
\hline   % ======================   graph analytics
\multirow{3}{*}{\rot{\textbf{Ana.}}}
  & HPC Scalable Graph Analysis & fixed & & Y & N& N& uniform & & N   \\
\cline{2-10}
  & Graphalytics & extracted & social network & Y& N& power law & & & N   \\
\hline
\hline   %  ======================  streaming
\multirow{2}{*}{\rot{\textbf{St.}}}
  & S2Gen & schema-driven & Social Network & Y & N & N & user-defined & RDF & N     \\
\cline{2-10}
  & RSPLab & schema-driven & Agnostic & Y & Y & N & user-defined & RDF & N     \\
%\cline{2-10}
%  & & & & & & & &  &   \\
\hline
\end{tabular} }
\label{tab:comparisonCharacteristicsB}
\end{sidewaystable}

@@

\begin{table}[h]
\scriptsize
\centering
\tbl{Overlapping of classes of generators} {
\begin{tabular}{| c | l | l | l | l | l | l | l | }
 \hline
           &  \textbf{Generator}
               & \textbf{\rot{General}}
               & \textbf{\rot{Semantic Web}}
               & \textbf{\rot{Graph databases\ }}
               & \textbf{\rot{Social networks}}
               & \textbf{\rot{Analytics}}
               & \textbf{\rot{Steaming}}
               \\ \hline
\hline   % ====================== general graphs
\multirow{6}{*}{\rot{\textbf{General}}}
  & \cite{barabasi1999emergence} & {\bf x} & & & & & \\
\cline{2-8}
   & R-MAt    & {\bf x} & & & & & \\
\cline{2-8}
  & GraphGen  & {\bf x} & & x & & & \\
\cline{2-8}
  & Graph 500 & {\bf x} & & & & & \\
\cline{2-8}
  & BTER      & {\bf x} & & & & & \\
\cline{2-8}
  & Darwini   & {\bf x} & & & & & \\
\hline
\hline %  ======================  Semantic web
\multirow{15}{*}{\rot{\textbf{Semantic web}}}
 & LUBM  & & {\bf x} & & & & \\
\cline{2-8}
 & LBBM  & & {\bf x} & & & & \\
\cline{2-8}
 & UOBM  & & {\bf x} & & & & \\
\cline{2-8}
 & IIMB & & {\bf x} & & & & \\
\cline{2-8}
 & BSBM & & {\bf x} & & & & \\
\cline{2-8}
 & SP$^2$Bench & & {\bf x} & & & & \\
\cline{2-8}
 & \cite{Duan:2011:AOC:1989323.1989340} & & {\bf x} & & & & \\
\cline{2-8}
 & DBPSB & & {\bf x} & & & & \\
\cline{2-8}
 & LODIB & & {\bf x} & & & & \\
\cline{2-8}
 & SIB & & {\bf x} & & & & \\
\cline{2-8}
 & Geographica & & {\bf x} & & & & \\
\cline{2-8}
 & WatDiv & & {\bf x} & & & & \\
\cline{2-8}
 & RBench & & {\bf x} & & & & \\
\cline{2-8}
 & LDBC SPB & & {\bf x} & & & & \\
\cline{2-8}
 & LinkGen & & {\bf x} & & & & \\
\hline
\hline  % ======================  graph databases
\multirow{3}{*}{\rot{\textbf{GDBs}}}
  & XGDBench & & & {\bf x} & x & & \\
\cline{2-8}
  & gMark & & x & {\bf x} & x & & \\
\cline{2-8}
  & graphGen & & & {\bf x} & & & \\
\hline
\hline %  ======================   social networks
\multirow{7}{*}{\rot{\textbf{SNs}}}
 & \cite{Barrett:2009:GAL:1995456.1995598} & & & & x & & \\
\cline{2-8}
 & \cite{Yao2011}  & & & & {\bf x} & & \\
\cline{2-8}
 & LinkBench  & & & x & {\bf x} & & \\
\cline{2-8}
 & S3G2  & & x & x & {\bf x} & & \\
\cline{2-8}
 & \cite{Sukthankar-SocialInfo2014}  & & & & {\bf x} & & \\
\cline{2-8}
 & LDBC SNB   & & x & x & {\bf x} & & \\
\cline{2-8}
  & \cite{Nettleton2016}  & & & & {\bf x} & & \\
\hline
\hline   % ======================   graph analytics
\multirow{2}{*}{\rot{\textbf{An.}}}
  & HPC Scalable Graph Analysis  & & & & & {\bf x} & \\
\cline{2-8}
  & Graphalytics & & & & & {\bf x} & \\
\hline
\hline   %  ======================  streaming
\multirow{2}{*}{\rot{\textbf{St.}}}
  & S2Gen & & & & & & {\bf x}\\
\cline{2-8}
  & RSPLab & & & & & & {\bf x} \\
%\cline{2-8}
%  & & & & & & \\
\hline
\end{tabular} }
\label{tab:overlapping}
\end{table}
